Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd
f

# Data
```{r}
load("FullDataSet.csv")
```

Re-Cleaned 
```{r}
FullDataSet <- FullDataSet %>% select(-c(median_rent))
```

@@

##Dataset Details 
```{r}
dim(FullDataSet)

names(FullDataSet)

head(FullDataSet)

summary(FullDataSet)

colnames(FullDataSet)
```

@@

>>>>

# Data
```{r}
Finaldata<- read.csv("FinalDataSet.csv")
```

Re-Cleaned 
```{r}
Finaldata <- Finaldata %>% select(-c(X,X.1)) 
```

@@

##Dataset Details 
```{r}
dim(Finaldata)

names(Finaldata)

head(Finaldata)

summary(Finaldata)

colnames(Finaldata)
```

##Variables of Interest

+------------------------+---------------------------------------------------+
| Variables:             | Meaning:                                          |
+========================+===================================================+
| `polyname`             | State Name                                        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `StateColor`           | Political Leaning                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_hispanic`      | Percent of the Population that is Hispanic        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_white`        | Percent of the Population that is White           |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_asian`        | Percent of the Population that is Asian           |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_black`        | Percent of Population that is Black               |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`total_population`      | Total State Population                            | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`per_capita_income`     | Income per Capita                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `Winner`               | Indicator for whether a Republican or Democrat Won| 
|                        |                                                   |  
+------------------------+---------------------------------------------------+
|`total_2016`            | Total Number of Votes                             | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+

@@

###Demographic 
```{r}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)
plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous( name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") +
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

#By Results 
plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Asian by General Election Results")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
) + facet_wrap(~Winner)

#By income 
plot_usmap(data = Finaldata, values = "per_capita_income", color = "white") + 
  scale_fill_continuous(low = "sky blue", high = "black", name = "$ Per Capita", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent Capita Income")+
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

ggplot(Finaldata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")

ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~StateColor)

ggplot(Finaldata, aes(x = percent_asian, y = percent_republican2016, color = Winner)) + 
    scale_color_manual(values = c("blue","purple","red")) + 
    geom_point(alpha = 0.8) + geom_text(aes(label=ifelse(percent_asian>.2,as.character(state),"")),hjust=1.2,vjust=0)+ geom_text(aes(label=ifelse(percent_republican2016<.2,as.character(state),"")),hjust=-.1,vjust=0) + ggtitle("Percent of Asians and Trump Support by Election Outcome") + xlab("Percent Asian") + ylab("Trump Support")

ggplot(Finaldata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Per Capita Income") + xlab("Per Capita Income") + ylab("Density") + facet_wrap(~Winner)
```
